Male-biased sexual selection, but not sexual dichromatism, predicts speciation in birds

### 2021-03-02 Sexual Selection and Speciation.Rmd
update supp mat with names

---
title: Male-biased sexual selection, but not sexual dichromatism, predicts speciation in birds
author: 
# "Justin G. Cally, Devi Stuart-Fox, Luke Holman, Iliana Medina Guzmán"
csl: References/evolution.csl
output:
  html_document:
    toc: true # table of content true
    toc_float: true # make 
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  ## if you want number sections at each table header
    theme: yeti # lovely fonts and colours
    code_folding: hide # awesome buttons to show/hide the code
subtitle: Electronic Supplementary Material
bibliography: References/SS_Extinction.bib
---

>>>>

---
title: Male-biased sexual selection, but not sexual dichromatism, predicts speciation in birds
author: "Justin G. Cally, Devi Stuart-Fox, Luke Holman, James Dale and Iliana Medina"
csl: References/evolution.csl
output:
  html_document:
    toc: true # table of content true
    toc_float: true # make 
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  ## if you want number sections at each table header
    theme: yeti # lovely fonts and colours
    code_folding: hide # awesome buttons to show/hide the code
subtitle: Electronic Supplementary Material
bibliography: References/SS_Extinction.bib
---
